Supplementary domain trees

### 2017-02-17 domain_level/tree_comparison_with_Bengtsson_and_Rask.Rmd
added in html updated domain rmd to include session info

##Load libraries
```{r}
library(ggtree)
library(ggplot2)
library(ape)
wd = "/home/users/allstaff/tonkin-hill.g/var_differential_analysis/domain_level/data"
```

@@

Lavsten et al 2012 also found DBLb3 to be more expressed in children with severe malaria.
```{r}
setwd(wd)

dbl_b3 <- read.tree("./compare_DBLb3/combined_vardom_severe_DBLb3.phylip")

@@

```{r}
setwd(wd)

tree <- read.tree("./compare_DC8/MA_combined_raskDBLd1_DBLd1s.fasta.phy")

@@

```{r}
setwd(wd)

tree <- read.tree("./compare_DC8/MA_combined_raskDBLb12_DBLb12s.fasta.phy")

@@

```{r}
setwd(wd)

tree <- read.tree("./compare_DC8/MA_combined_raskCIDRb1_CIDRb1s.fasta.phy")

>>>>

##Load libraries
```{r}
library(ggplot2)
library(ape)
```

@@

Lavsten et al 2012 also found DBLb3 to be more expressed in children with severe malaria.
```{r}
dbl_b3 <- read.tree("./data/compare_DBLb3/combined_vardom_severe_DBLb3.phylip")

@@

```{r}
tree <- read.tree("./data/compare_DC8/MA_combined_raskDBLd1_DBLd1s.fasta.phy")

@@

```{r}
tree <- read.tree("./data/compare_DC8/MA_combined_raskDBLb12_DBLb12s.fasta.phy")

@@

```{r}
tree <- read.tree("./data/compare_DC8/MA_combined_raskCIDRb1_CIDRb1s.fasta.phy")
